Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
Make some small fixes

In \term{Helios}, the public ballot is a hash of an encryption. \term{Helios} uses ElGamal to encrypt ballots,
which -- unlike \term{Scantegrity}'s core \emph{random} Table P -- could be subject to attack, given that
ElGamal is a published encryption function. Similarly, \term{Helios} uses the standard SHA-1 hash algorithm
to hash encrypted ballots. Note that we are not making a precise quantification about \term{Helios}'s
security: rather, we simply note that the difference between these two systems can be thought of as
a tradeoff between key size and privacy guarantees.

With \term{\pv{}}, the submitted ballot is really just a position within a permutation of the
candidates. The \emph{position} within the permutation is not encrypted: rather, the candidate
permutation is secret and can be obtained (later in the election process) from the onion.

>>>>

In \term{Helios}, the public ballot is a hash of an encryption. \term{Helios} uses ElGamal to encrypt ballots,
which -- unlike \term{Scantegrity}'s core \emph{random} Table P -- could be subject to attack, given that
ElGamal is a published encryption function. Similarly, \term{Helios} uses the standard SHA-1 hash algorithm
to hash encrypted ballots. Note that we are not making a precise quantification about \term{Helios}'s
security. Rather, we simply note that the difference between these two systems can be thought of as
a tradeoff between key size and privacy guarantees.

With \term{\pv{}}, the submitted ballot is the selected candidate's position within a permutation of
the candidates. The \emph{position} within the permutation is not encrypted; rather, the permutation
itself is secret and can be obtained (later in the election process) from the onion.
